Large-Scale Content-Based Matching of MIDI and Audio Files

### 2015-04-30 paper.tex
Change P to p, q

We then use dynamic time warping to find the lowest-cost path through a full pairwise cosine similarity matrix $S \in \mathbb{R}^{N \times M}$ of the MIDI and audio CQTs.
This path can be represented as a sequence $P \in \mathbb{R}^L$ of tuples of indices from each sequence such that $P[n] = (p, q)$ implies that the $p$th MIDI beat should be aligned to the $q$th audio beat.
Traditional DTW requires that this path includes the start and end of each sequence, or equivalently that $P[1] = (1, 1)$ and $P[L] = (N, M)$.
This approach is not valid when one sequence may be a subsequence of the other, which is often true in our problem setting due to the fact that the MSD 7digital audio recordings are cropped preview clips of the entire recordings.
We therefore modify this constraint so that if $P[L] = (p, q)$ then either $gN \le p \le N$ or $gM \le q \le M$ where $g \approx 1$ is a parameter which provides a small amount of additional tolerance.
We also include the typical modification of applying an additive penalty for ``non-diagonal moves'', i.e. path entries where if $P[n] = (p, q)$ then $P[n + 1] = (p, r)$ or $P[n] = (r, q)$.
For synthesized MIDI-to-audio alignment, we used $g = .95$ and set the non-diagonal additive penality to the 90th percentile of $S$.

@@

\subsection{Splitting the subset}`

>>>>

We then use dynamic time warping to find the lowest-cost path through a full pairwise cosine similarity matrix $S \in \mathbb{R}^{N \times M}$ of the MIDI and audio CQTs.
This path can be represented as two sequences $p, q \in \mathbb{R}^L$ of indices from each sequence such that $p[i] = n, q[i] = m$ implies that the $n$th MIDI beat should be aligned to the $m$th audio beat.
Traditional DTW requires that this path includes the start and end of each sequence, or equivalently that $p[1] = q[1] = 1; p[L] = N; p[L] = M$.
This approach is not valid when one sequence may be a subsequence of the other, which is often true in our problem setting due to the fact that, for example, the MSD 7digital audio recordings are cropped preview song clips.
We therefore modify this constraint so that either $gN \le p[L] \le N$ or $gM \le q[L] \le M$ where $g \approx 1$ is a parameter which provides a small amount of additional tolerance.
We also include the typical modification of applying an additive penalty for ``non-diagonal moves'', i.e. path entries where either $p[i] = p[i + 1]$ or $q[i] = q[i + 1]$.
For synthesized MIDI-to-audio alignment, we used $g = .95$ and set the non-diagonal additive penality to the 90th percentile of $S$.

@@

\subsection{Splitting the subset}
